The state of knowledge for marine invertebrate biodiversity in the continental US

### 2018-01-17 manuscript.Rmd
[fix #80] add discussion about gradients

Spatial distribution of species richness with latitude differ markedly between the Pacific and the Atlantic coasts. On the Pacific coast, richness is lowest around 40° of latitude, whereas on the Atlantic coast, it is highest at the same latitude (Fig. \@ref(fig:map-diversity-sampling)B, Fig. \@ref(fig:latitudinal-gradient)).

Talk about contributions of different institutions here

>>>>

Spatial distribution of species richness with latitude differ between the Pacific and the Atlantic coasts. On the Pacific coast, the recorded richness is lowest around 40° of latitude, whereas on the Atlantic coast, it is highest at the same latitude (Fig. \@ref(fig:map-diversity-sampling)B, Fig. \@ref(fig:latitudinal-gradient)B). These trends are however strongly driven by sampling effort (Fig. \@ref(fig:latitudinal-gradient)C). Notably, for the Pacific coast, there is a deficit in the number of samples between 40° and 45° of latitude corresponding to the state of Oregon. In contrast, the peak in number of species observed and in the number of records around 42° on the Atlantic coast can be attributed to the presence of the Woods Hole Oceanographic Institute.
